Sparsely Activated Networks

### 2020-06-04 ms.tex
simplify repo

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys_values}{keys_values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{"images_1d/UCI-epilepsy_identity_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"images_1d/UCI-epilepsy_relu_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"images_1d/UCI-epilepsy_topk_absolutes_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"images_1d/UCI-epilepsy_extrema_pool_indices_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"images_1d/UCI-epilepsy_extrema_1d_2_activations_0"}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{"images_2d/MNIST_identity_2d_2_activations_1"}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{"images_2d/MNIST_relu_2d_2_activations_0"}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{"images_2d/MNIST_topk_absolutes_2d_2_activations_0"}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{"images_2d/MNIST_extrema_pool_indices_2d_2_activations_0"}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{"images_2d/MNIST_extrema_2d_2_activations_0"}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_signal"}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_reconstructed"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_reconstruction_0"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_activations_0"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_similarity_0"}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_1d/UCI-epilepsy_extrema_1d_2_kernel_0"}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_signal"}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_reconstructed"}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_reconstruction_0"}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_activations_0"}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_similarity_0"}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_1d/UCI-epilepsy_extrema_1d_2_kernel_0"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_reconstruction_1"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_activations_1"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_1d/UCI-epilepsy_extrema_1d_2_similarity_1"}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_1d/UCI-epilepsy_extrema_1d_2_kernel_1"}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_signal"}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_reconstructed"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_reconstruction_0"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_activations_0"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_similarity_0"}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_2d/MNIST_extrema_2d_2_kernel_0"}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_signal"}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_reconstructed"}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_reconstruction_0"}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_activations_0"}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_similarity_0"}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_2d/MNIST_extrema_2d_2_kernel_0"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_reconstruction_1"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_activations_1"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"images_2d/MNIST_extrema_2d_2_similarity_1"}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"images_2d/MNIST_extrema_2d_2_kernel_1"}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/apnea-ecg"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/bidmc"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/bpssrat"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/cebsdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/ctu-uhb-ctgdb"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/drivedb"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/emgdb"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/mitdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/noneeg"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/prcp"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/shhpsgdb"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/slpdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/sufhsdb"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/voiced"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/wrist"}
	\includegraphics[width=0.245\textwidth]{"images_mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list/legend"}
	\caption{Inverse compression ratio ($CR^{-1}$) vs. normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}
	\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{"images_1d/crrl_density_plot"}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{"images_1d/mean_flithos_validation_epochs"}\label{subfig:flithos_epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{"images_1d/mean_flithos_variable_kernel_size_list"}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}
	\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{"images_1d/apnea-ecg_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bidmc_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bpssrat_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/cebsdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/ctu-uhb-ctgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/drivedb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/emgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/mitdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/noneeg_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/prcp_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/shhpsgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/slpdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/sufhsdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/voiced_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/wrist_relu_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"images_1d/apnea-ecg_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bidmc_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bpssrat_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/cebsdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/ctu-uhb-ctgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/drivedb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/emgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/mitdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/noneeg_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/prcp_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/shhpsgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/slpdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/sufhsdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/voiced_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/wrist_topk_absolutes_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"images_1d/apnea-ecg_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bidmc_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bpssrat_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/cebsdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/ctu-uhb-ctgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/drivedb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/emgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/mitdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/noneeg_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/prcp_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/shhpsgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/slpdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/sufhsdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/voiced_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/wrist_extrema_pool_indices_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"images_1d/apnea-ecg_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bidmc_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/bpssrat_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"images_1d/cebsdb_extrema_1d_1_kernel_0"}

>>>>

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys_values}{results/keys_values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{"results/UCI-epilepsy_identity_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"results/UCI-epilepsy_relu_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"results/UCI-epilepsy_topk_absolutes_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"results/UCI-epilepsy_extrema_pool_indices_1d_2_activations_0"}}
	\subfloat{\includegraphics[width=0.2\textwidth]{"results/UCI-epilepsy_extrema_1d_2_activations_0"}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{"results/MNIST_identity_2d_2_activations_1"}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{"results/MNIST_relu_2d_2_activations_0"}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{"results/MNIST_topk_absolutes_2d_2_activations_0"}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{"results/MNIST_extrema_pool_indices_2d_2_activations_0"}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{"results/MNIST_extrema_2d_2_activations_0"}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_signal"}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_reconstructed"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_reconstruction_0"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_activations_0"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_similarity_0"}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/UCI-epilepsy_extrema_1d_2_kernel_0"}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_signal"}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_reconstructed"}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_reconstruction_0"}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_activations_0"}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_similarity_0"}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/UCI-epilepsy_extrema_1d_2_kernel_0"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_reconstruction_1"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_activations_1"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/UCI-epilepsy_extrema_1d_2_similarity_1"}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/UCI-epilepsy_extrema_1d_2_kernel_1"}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_signal"}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_reconstructed"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_reconstruction_0"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_activations_0"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_similarity_0"}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/MNIST_extrema_2d_2_kernel_0"}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_signal"}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_reconstructed"}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_reconstruction_0"}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_activations_0"}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_similarity_0"}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/MNIST_extrema_2d_2_kernel_0"}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_reconstruction_1"}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_activations_1"}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{"results/MNIST_extrema_2d_2_similarity_1"}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{"results/MNIST_extrema_2d_2_kernel_1"}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_apnea-ecg"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_bidmc"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_bpssrat"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_cebsdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_ctu-uhb-ctgdb"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_drivedb"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_emgdb"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_mitdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_noneeg"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_prcp"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_shhpsgdb"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_slpdb"}
	\\
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_sufhsdb"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_voiced"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_wrist"}
	\includegraphics[width=0.245\textwidth]{"results/mean_inverse_compression_ratio_vs_mean_reconstruction_loss_variable_kernel_size_list_legend"}
	\caption{Inverse compression ratio ($CR^{-1}$) vs. normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}
	\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{"results/crrl_density_plot"}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{"results/mean_flithos_validation_epochs"}\label{subfig:flithos_epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{"results/mean_flithos_variable_kernel_size_list"}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}
	\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{"results/apnea-ecg_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bidmc_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bpssrat_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/cebsdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/ctu-uhb-ctgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/drivedb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/emgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/mitdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/noneeg_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/prcp_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/shhpsgdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/slpdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/sufhsdb_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/voiced_relu_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/wrist_relu_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"results/apnea-ecg_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bidmc_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bpssrat_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/cebsdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/ctu-uhb-ctgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/drivedb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/emgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/mitdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/noneeg_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/prcp_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/shhpsgdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/slpdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/sufhsdb_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/voiced_topk_absolutes_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/wrist_topk_absolutes_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"results/apnea-ecg_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bidmc_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bpssrat_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/cebsdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/ctu-uhb-ctgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/drivedb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/emgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/mitdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/noneeg_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/prcp_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/shhpsgdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/slpdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/sufhsdb_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/voiced_extrema_pool_indices_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/wrist_extrema_pool_indices_1d_1_kernel_0"}

@@

	\includegraphics[width=0.06\textwidth]{"results/apnea-ecg_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bidmc_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/bpssrat_extrema_1d_1_kernel_0"}
	\includegraphics[width=0.06\textwidth]{"results/cebsdb_extrema_1d_1_kernel_0"}
